Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex

\begin{figure}
\includegraphics[width=\textwidth]{pg_0004}
\caption{\label{fig4}The scores of systems with colocation window between 2 and 4, cooccurrence handling on, \naive{} Bayes classifier and dependency parsing off are presented here. Each plotted number corresponds to a system, and the number refers to the colocation window}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{pg_0004}
\caption{\label{fig4}The scores of systems with collocation window between 2 and 4, cooccurrence handling on, \naive{} Bayes classifier and dependency parsing off are presented here. Each plotted number corresponds to a system, and the number refers to the collocation window}
\end{figure}
